Scheeper's Meager-NWD Game and the Menger Game

### 2014-05-14 phd/dissertation/_raw_chapter4.tex
Finish ch 2 draft, outline of results for ch 3, ch 6

\documentclass[11pt]{article}

\pdfpagewidth 8.5in
\pdfpageheight 11in

\setlength\topmargin{0in}
\setlength\headheight{0in}
\setlength\headsep{0.2in}
\setlength\textheight{8in}
\setlength\textwidth{6in}
\setlength\oddsidemargin{0in}
\setlength\evensidemargin{0in}
\setlength\parindent{0.25in}
\setlength\parskip{0.1in}

\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amsthm}

      \theoremstyle{plain}
      \newtheorem{theorem}{Theorem}
      \newtheorem{lemma}[theorem]{Lemma}
      \newtheorem{corollary}[theorem]{Corollary}
      \newtheorem{proposition}[theorem]{Proposition}
      \newtheorem{conjecture}[theorem]{Conjecture}
      \newtheorem{question}[theorem]{Question}
      \newtheorem{example}[theorem]{Example}

      \theoremstyle{definition}
      \newtheorem{definition}[theorem]{Definition}

      \theoremstyle{remark}
      \newtheorem{remark}[theorem]{Remark}

% Strategy uparrow shortcuts
\newcommand{\prewin}{\uparrow_{\text{pre}}}
\newcommand{\markwin}{\uparrow_{\text{mark}}}
\newcommand{\tactwin}{\uparrow_{\text{tact}}}
\newcommand{\ktactwin}[1]{\uparrow_{#1\text{-tact}}}
\newcommand{\kmarkwin}[1]{\uparrow_{#1\text{-mark}}}
\newcommand{\codewin}{\uparrow_{\text{code}}}
\newcommand{\limitwin}{\uparrow_{\text{limit}}}

\begin{document}

\centerline{\bf PhD Research Results}
\centerline{Steven Clontz}

\begin{definition} Some notation on games of length $\omega$:

\begin{itemize}
\item A \textbf{game of length $\omega$} consists of two \textbf{Players} I and II. On \textbf{round} $n$ of $\omega$, Player I first takes a \textbf{turn} choosing an element of some set $X$, followed by Player II taking a turn choosing an element from some set $Y$.

\item A \textbf{move} by a player is the selection that player makes during a particular round.

\item A \textbf{rule} for a Player in a game is a condition on that player's move during each round. A move is said to be \textbf{legal} if it doesn't violate the rule.

\item A \textbf{play} by Player I is a sequence $\left<x_0,x_1,\dots\right> \in X^\omega$ (and similar for Player II). It is said to be \textbf{legal} if each move is legal. A finite initial sequence of a play is called a \textbf{partial play}.

\item A \textbf{strategy} for a Player is a function which has all possible partial plays by the opposing player as its domain. It denotes the choice for that Player on each turn. It is said to be \textbf{legal} if it yields only legal moves when the opposing player makes only legal moves.

\item A \textbf{counter} to a legal strategy by a Player is a function which has as its domain the turn number and the other player's strategy. It is said to be \textbf{legal} if it only yields legal moves.

\item A \textbf{winning condition} is some condition on the plays made by both players.

\item At the conclusion of a game, if all moves are legal, then Player I \textbf{wins} the game if the winning condition is satisfied, and Player II wins the game otherwise. (Should any move be illegal, then the first player to make an illegal move loses the game to the other player.)
\end{itemize}
\end{definition}

When the sets $X,Y$ are related to a topological space, it is said to be a \textbf{topological game}. The presence or absense of a ``winning'' strategy for one player or another characterizes a property of the space.

\begin{definition}
A strategy for Player A is said to be a \textbf{winning strategy} if there does not exist a counter which allows the other player to win the game. If Player Z has a winning strategy for the game $G$, this can be denoted $Z \uparrow G$.
\end{definition}

Proofs showing the existance of a winning strategy typically define the winning strategy, and then show that it defeats every possible play by the opponent. Proofs showing the nonexistance of a winning strategy typically define the counter to any arbitrary strategy.

In the mid 1980s, Dr. Gary Gruenhage defined the following topological games.

\begin{definition}
The \textbf{compact-point game on a topological space $X$} is denoted $G_{K,P}(X)$. During round $n$, Player I (called $K$) chooses a compact set $K_n\in K[X]$, and Player II (called $P$) chooses a point $x_n\in X$. $K$ must follow the rule that $K_{n+1}\supseteq K_n$, while $P$ must follow the rule that $x_n\not\in K_n$. The winning condition for $K$ is that the collection of singletons chosen by $P$, $\{\{x_n\} : n<\omega\}$, must be locally finite everywhere in the space. (This is equivalent to the set $\{x_n : n<\omega\}$ lacking a cluster point.)
\end{definition}

\begin{definition}
The \textbf{compact-compact game on a topological space $X$} is denoted $G_{K,L}(X)$. During round $n$, Player I (called $K$) chooses a compact set $K_n\in K[X]$, and Player II (called $L$) also chooses a compact set $L_n\in K[X]$. $K$ must follow the rule that $K_{n+1}\supseteq K_n$, while $P$ must follow the rule that $L_n\cap K_n=\emptyset$. The winning condition for $K$ is that the collection of compact sets chosen by $L$, $\{L_n : n<\omega\}$, must be locally finite everywhere in the space.
\end{definition}

An interesting property of the game $G_{K,L}(X)$ is the following result, proven by Gruenhage in his paper \textit{Games Covering Properties and Eberlein Compacts}.

\begin{theorem}
The following are equivalent for a locally compact space $X$:
    \begin{itemize}
    \item $X$ is paracompact
    \item $K \uparrow G_{K,L}(X)$.
    \end{itemize}
\end{theorem}

@@

\begin{definition}
A \textbf{limited information strategy} for a game is a function whose domain is restricted to less information than all previous moves by the opposing player.
\end{definition}

@@

\begin{definition}
A \textbf{tactical strategy} considers only the most recent move by the opposing player. If Player $Z$ has a winning tactical strategy for a game $G$, this may be denoted $Z \uparrow_{\text{tact}} G$.
\end{definition}

\begin{definition}
A \textbf{Markov strategy} considers only the most recent move by the opposing player and the turn number. If Player $Z$ has a winning Markov strategy for a game $G$, this may be denoted $Z \uparrow_{\text{mark}} G$.
\end{definition}

\begin{theorem}
The following are equivalent for a locally compact space $X$:
    \begin{itemize}
    \item $X$ is metacompact
    \item $K \uparrow_{\text{tact}}G_{K,P}(X)$.
    \end{itemize}
\end{theorem}

\begin{theorem}
The following are equivalent for a locally compact space $X$:
    \begin{itemize}
    \item $X$ is $\sigma$-metacompact
    \item $K \uparrow_{\text{mark}}G_{K,P}(X)$.
    \end{itemize}
\end{theorem}

@@

\begin{definition}
A \textbf{predetermined strategy} considers only the turn number. If Player $Z$ has a winning predetermined strategy for a game $G$, this may be denoted $Z \prewin G$.
\end{definition}

@@

\begin{definition}
A \textbf{button-mashing strategy} is a constant function. If Player $Z$ has a winning button-mashing strategy for a game $G$, this may be denoted $Z \uparrow_{\text{mash}} G$.
\end{definition}

\begin{proposition}
The following are equivalent for any space $X$:
    \begin{itemize}
    \item $X$ is compact
    \item $K \uparrow_{\text{mash}}G_{K,P}(X)$.
    \end{itemize}
\end{proposition}

@@

\begin{proposition}
If $K \prewin G_{K,P}(X)$, then $X$ is $\sigma$-compact.
\end{proposition}

@@

\begin{theorem}
If $Y$ is a locally compact, Lindel\"of space, then $K \prewin G_{K,P}(X)$.
\end{theorem}

@@

\begin{corollary}
The following are equivalent for a locally compact space $X$:
    \begin{itemize}
    \item $X$ is $\sigma$-compact
    \item $X$ is Lindel\"of
    \item $K \prewin G_{K,P}(X)$.
    \end{itemize}
\end{corollary}

@@

\begin{definition}
Let $M=\omega^2\cup\{\infty\}$ denote the \textbf{metric fan space} with the topology generated by the singletons in $\omega^2$ and sets of the form $((\omega\setminus n)\times\omega) \cup \{\infty\}$ for $n<\omega$.
\end{definition}

\begin{proposition}
For each compact set $C$ in $M$, there exists a minimal dominating function $f_C$ such that for each $(x,y)\in C\setminus\{\infty\}$, $f(x)> y$.
\end{proposition}

\begin{lemma}
$P \markwin G_{K,P}(M)$ where $M$ is the metric fan space. (This implies $K\not\uparrow G_{K,P}(M)$.)
\end{lemma}

@@

\begin{theorem}
Every first-countable non-locally countably compact space has the metric fan space $M$ as a closed subspace.
\end{theorem}

@@

\begin{corollary}
$P \markwin G_{K,P}(X)$ where $X$ is a first-countable non-locally countably compact space. (This implies $K\not\uparrow G_{K,P}(X)$.)
\end{corollary}

@@

\begin{theorem}
$P \not\tactwin D_{K,P}(M)$ where $M$ is the metric fan space.
\end{theorem}

@@

\begin{definition}
A space $X$ is \textbf{hemicompact} if there exists a chain of increasing compact sets $K_0\subseteq K_1 \subseteq \dots$ such that every compact set in $X$ is a subset of some $K_n$.
\end{definition}

\begin{lemma}
If $K\prewin G_{K,P}(X)$, then $X$ is hemicompact. Furthermore, any predetermined winning strategy for $K$ witnesses hemicompactness.
\end{lemma}

@@

\begin{theorem}
The following are equivalent for any locally compact space $X$:
  \begin{itemize}
  \item $X$ is hemicompact.
  \item $K \prewin G_{K,L}(X)$.
  \item $K \prewin G_{K,P}(X)$.
  \end{itemize}
\end{theorem}

@@

\begin{corollary}
The following are equivalent for any locally compact space $X$:
  \begin{itemize}
  \item $X$ is Lindel\"of.
  \item $X$ is $\sigma$-compact.
  \item $X$ is hemicompact.
  \item $K \prewin G_{K,L}(X)$.
  \item $K \prewin G_{K,P}(X)$.
  \end{itemize}
\end{corollary}

@@

\begin{definition}
A topological space is called a \textbf{$k$-space} if the following condition is satisfied: \[C \subseteq X \text{ is closed in } X\, \Leftrightarrow \, C\cap K \text{ is closed in } K \text{ for all compact sets } K\in K[X]\]
\end{definition}

\begin{definition}
A topological space is called a \textbf{$k_\omega$-space} if there exist $K_0,K_1,\dots \in K[X]$ that satisfy the following condition: \[C \subseteq X \text{ is closed in } X\, \Leftrightarrow \, C \cap K_n \text{ is closed in } K_n \text{ for all } n\]
\end{definition}

\begin{theorem}
The following are equivalent for any Hausdorff $k$-space $X$:
  \begin{itemize}
  \item $X$ is hemicompact.
  \item $X$ is $k_{\omega}$.
  \item $K \prewin G_{K,P}(X)$.
  \end{itemize}
Furthermore, all predetermined strategies for $K$ witness hemicompact and $k_\omega$, and any witness to hemicompact/$k_\omega$ witnesses the other and serves as a predetermined strategy for $K$.
\end{theorem}

@@

\begin{theorem}
For any hemicompact Hausdorff $k$-space $X$, $K \prewin G_{K,L}(X)$.
\end{theorem}

@@

\begin{corollary}
The following are equivalent for any Hausdorff $k$-space $X$:
  \begin{itemize}
  \item $X$ is hemicompact.
  \item $X$ is $k_{\omega}$.
  \item $K$ has a winning predetermined strategy in $G_{K,L}(X)$.
  \item $K$ has a winning predetermined strategy in $G_{K,P}(X)$.
  \end{itemize}
\end{corollary}

@@

\begin{definition}
Given a set $X$, an ultrafilter on $X$ is a collection $\mathcal{F}\subseteq\mathcal{P}(X)$ such that
    \begin{enumerate}
    \item $\emptyset\not\in \mathcal{F}$
    \item $A,B\in\mathcal{F} \Rightarrow A\cap B \in \mathcal{F}$
    \item $A\in\mathcal{F}$ and $A \subseteq B$ $\Rightarrow$ $B\in\mathcal{F}$
    \item $\forall A \subseteq X(A\in\mathcal{F}$ or $X\setminus A \in \mathcal{F})$
    \end{enumerate}
As a result, ultrafilters which contain a finite set contain only one singleton (and are called \textbf{principal}). Otherwise, ultrafilters which contain no finite sets are called \textbf{free}.
\end{definition}

\begin{definition}
The \textbf{Stone-Cech compactification} $\beta\omega$ of $\omega$ is the collection of ultrafilters on $\omega$. The principal ultrafilters containing a singleton $\{n\}$ are each identified with $n$ itself and are isolated. Free ultrafilters $\mathcal{F}$ are given neighborhoods of the form \[\{\mathcal{G} : \mathcal{G} \text{ is an ultrafilter on } \omega \text{ and } A \in \mathcal{G}\} = A \cup \{\mathcal{G}: \mathcal{G} \text{ is a free ultrafilter on } \omega \text{ and } A \in \mathcal{G}\}\] for each $A\in\mathcal{F}$.

Alternately $\beta\omega=\omega\cup\{\mathcal{F} : \mathcal{F}$ is a free ultrafilter on $\omega\}$ where $\omega$ is discrete and the free ultrafilters have the local base described above.
\end{definition}

\begin{definition}
A \textbf{single-ultrafilter space} is a subset of $\beta\omega$ containing all elements of $\omega$ and a single ultrafilter $\mathcal{F}$.
\end{definition}

\begin{proposition}
The compact sets of a single-ultrafilter space are exactly the finite subsets of the space. Thus a single-ultrafilter space is neither locally compact nor $k$.
\end{proposition}

@@

\begin{proposition}
If $X$ is any single-ultrafilter space with the ultrafilter $\mathcal{F}$, then $K\not\prewin G_{K,L}(X)$.
\end{proposition}

@@

\begin{proposition} 
If a selective ultrafilter $\mathcal{F}$ exists (this is independent of ZFC), then $K$ has no winning predetermined strategy in the compact-point game $G_{K,P}(Y)$ for the single selective ultrafilter space $Y=\omega \cup \{\mathcal{F}\}$.
\end{proposition}

@@

\begin{theorem}
Let $a_n$ be a sequence such that the sequence $\frac{a_n}{n}$ is unbounded above. Then there is an ultrafilter $\mathcal{F}$ such that $\sigma(n)=(\sum_{m\leq n} a_m )\cup \{\mathcal{F}\}$ is a winning predetermined strategy for $K$ in $G_{K,P}(\omega\cup\{\mathcal{F}\})$.
\end{theorem}

@@

\begin{question}
$K \prewin G_{K,L}(X) \Rightarrow X$ is a $k$-space?
\end{question}

\centerline{\bf Another game: $Con_{O,P}(X,x)$}

\begin{definition} 
Gruenhage's open-point convergence game $Con_{O,P}(X,x)$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$. $O$ wins if the points chosen by $P$ converge to $x$.
\end{definition}

\begin{definition}
The one-point compactification of a space $X$ is $X\cup\{\infty\}$, where neighborhoods of points in $X$ are the same as they were originally, and neighborhoods of $\infty$ are sets $X\cup\{\infty\}\setminus K$ for compact $K$. If $X$ is discrete then neighborhoods of $\infty$ are cofinite sets containing $\infty$. 
\end{definition}

\begin{proposition}
$O\not\prewin Con_{O,P}(\kappa\cup\{\infty\},\infty)$, where $\kappa\cup\{\infty\}$ is the one-point compactification of discrete $\kappa\geq\omega_1$.
\end{proposition}

\begin{proof}
Given a predetermined strategy $\sigma(n)$ for $O$, $P$ simply chooses any ordinal in $\bigcap_{n<\omega} \sigma(n)$ to play on every turn.
\end{proof}

\begin{definition}
A \textbf{coding strategy} considers only the most recent move by each player. If Player $Z$ has a winning coding strategy for a game $G$, this may be denoted $Z \codewin G$.
\end{definition}

\begin{proposition}
$O\codewin Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for any cardinal $\kappa$. 
\end{proposition}

\begin{proof}
Define $\sigma(U,p)=U\setminus\{p\}$. A legal play by $P$ must never repeat the same point, so legal plays by $P$ converge to $\infty$.
\end{proof}

\begin{proposition}
$O\not\tactwin Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
\end{proposition}

\begin{proof}
Let $F(\alpha)$ be the complement of a tactical strategy for $O$. There exists some $n<\omega$ such that we may find an infinite $B\subseteq \omega_1$ with $n\not\in F(\beta)$ for $\beta\in B$ - if not, we may find uncountable ordinals $\alpha$ such that $\omega \subseteq F(\alpha)$, a contradiction. Choose $\beta\in B\setminus F(n)$, and note that repeating $n,\beta$ is a successful counter to $O$'s strategy.
\end{proof}

\begin{definition}
A \textbf{$k$-tactical strategy} considers only the last $k$ moves by the opposing player. If Player $Z$ has a winning $k$-tactical strategy for a game $G$, this may be denoted $Z \ktactwin{k} G$.
\end{definition}

\begin{theorem}
$O\not\ktactwin{k}Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
\end{theorem}

\begin{proof}
Let $\sigma:[\omega_1]^{\leq k}\to[\omega_1]^{<\omega}$ be a $k$-tactical strategy for $O$ restricted to $\omega_1$ and $F(S)=\omega_1\setminus\sigma(S)$.

Let $W_0=\omega_1$. We define $W_\alpha$ recursively as follows:
    \begin{itemize}
    \item For successor ordinals $\alpha+1$, let $\beta$ be the least element of $W_\alpha$ such that $[\beta+1,\omega_1) \cap \bigcup_{S\leq \beta} F(S)$ is nonempty, where $S \leq \beta$ is shorthand for $\{S \in [\omega_1]^{\leq k} : \forall \gamma \in S(\gamma < \beta)\}$. If no such $\beta$ exists, let $W_{\alpha+1}=W_\alpha$ and otherwise let $W_{\alpha+1}=W_\alpha \setminus \left([\beta+1,\omega_1) \cap \bigcup_{S\leq \beta} F(S)\right)$.
    \item For limit ordinals $\alpha$, let $W_\alpha = \bigcap_{\beta<\alpha} W_\beta$.
    \end{itemize}

Finally let $W=\bigcap_{\alpha<\omega_1}W_\alpha$ and observe that it is unbounded. Let $R$ collect all ordinals $\alpha\in W$ such that there is an ordinal $\beta$ where for all $S\in[W\cap(\beta,\omega_1)]^{\leq k}$, $\alpha \in F(S)$. It is easily seen that $R$ is finite. Let $0^*$ be the least element of $W\setminus R$.

Now, define a strictly increasing sequence of ordinals $\left<\alpha_1,\alpha_2,\alpha_3,\alpha_4,\dots\right>$ such that $\alpha_i \in W$ and $0^* \not\in F(\{\alpha_{2i+1},\dots,\alpha_{2i+k}\})$ for all $i$. The play $\left<0^*,\alpha_1,\dots,\alpha_k,0^*,\alpha_{k+1},\dots,\alpha_{2k},0^*,\dots\right>$ then defeats the strategy $\sigma$.
\end{proof}

Peter J. Nyikos has shown the following:

\begin{theorem}
$O\not\markwin Con_{O,P}(\omega_1\cup\{\infty\},\infty)$.
\end{theorem}

This can be improved:

\begin{theorem}
$O\not\kmarkwin{k} Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
\end{theorem}

\begin{proof}
Let $F:[\omega_1]^{\leq k}\times\omega\to[\omega_1]^{<\omega}$ be the complement of a $k$-Markov strategy for $O$ restricted to $\omega_1$.

>>>>

%!TEX root = dissertation.tex
% ^ leave for LaTeXTools build functionality

\chapter{Locally Finite Games}

Results pertaining to the Locally Finite game related to the W games.

\section{basic results}

\begin{thm}
The following are equivalent for a locally compact space $X$:
    \begin{itemize}
    \item $X$ is paracompact
    \item $K \uparrow G_{K,L}(X)$.
    \end{itemize}
\end{thm}

@@

\begin{defn}
A \textbf{limited information strategy} for a game is a function whose domain is restricted to less information than all previous moves by the opposing player.
\end{defn}

@@

\begin{defn}
A \textbf{tactical strategy} considers only the most recent move by the opposing player. If Player $Z$ has a winning tactical strategy for a game $G$, this may be denoted $Z \uparrow_{\text{tact}} G$.
\end{defn}

\begin{defn}
A \textbf{Markov strategy} considers only the most recent move by the opposing player and the turn number. If Player $Z$ has a winning Markov strategy for a game $G$, this may be denoted $Z \uparrow_{\text{mark}} G$.
\end{defn}

\begin{thm}
The following are equivalent for a locally compact space $X$:
    \begin{itemize}
    \item $X$ is metacompact
    \item $K \uparrow_{\text{tact}}G_{K,P}(X)$.
    \end{itemize}
\end{thm}

\begin{thm}
The following are equivalent for a locally compact space $X$:
    \begin{itemize}
    \item $X$ is $\sigma$-metacompact
    \item $K \uparrow_{\text{mark}}G_{K,P}(X)$.
    \end{itemize}
\end{thm}

@@

\begin{defn}
A \textbf{predetermined strategy} considers only the turn number. If Player $Z$ has a winning predetermined strategy for a game $G$, this may be denoted $Z \prewin G$.
\end{defn}

@@

\begin{defn}
A \textbf{button-mashing strategy} is a constant function. If Player $Z$ has a winning button-mashing strategy for a game $G$, this may be denoted $Z \uparrow_{\text{mash}} G$.
\end{defn}

\begin{prop}
The following are equivalent for any space $X$:
    \begin{itemize}
    \item $X$ is compact
    \item $K \uparrow_{\text{mash}}G_{K,P}(X)$.
    \end{itemize}
\end{prop}

@@

\begin{prop}
If $K \prewin G_{K,P}(X)$, then $X$ is $\sigma$-compact.
\end{prop}

@@

\begin{thm}
If $Y$ is a locally compact, Lindel\"of space, then $K \prewin G_{K,P}(X)$.
\end{thm}

@@

\begin{cor}
The following are equivalent for a locally compact space $X$:
    \begin{itemize}
    \item $X$ is $\sigma$-compact
    \item $X$ is Lindel\"of
    \item $K \prewin G_{K,P}(X)$.
    \end{itemize}
\end{cor}

@@

\begin{defn}
Let $M=\omega^2\cup\{\infty\}$ denote the \textbf{metric fan space} with the topology generated by the singletons in $\omega^2$ and sets of the form $((\omega\setminus n)\times\omega) \cup \{\infty\}$ for $n<\omega$.
\end{defn}

\begin{prop}
For each compact set $C$ in $M$, there exists a minimal dominating function $f_C$ such that for each $(x,y)\in C\setminus\{\infty\}$, $f(x)> y$.
\end{prop}

\begin{lem}
$P \markwin G_{K,P}(M)$ where $M$ is the metric fan space. (This implies $K\not\uparrow G_{K,P}(M)$.)
\end{lem}

@@

\begin{thm}
Every first-countable non-locally countably compact space has the metric fan space $M$ as a closed subspace.
\end{thm}

@@

\begin{cor}
$P \markwin G_{K,P}(X)$ where $X$ is a first-countable non-locally countably compact space. (This implies $K\not\uparrow G_{K,P}(X)$.)
\end{cor}

@@

\begin{thm}
$P \not\tactwin D_{K,P}(M)$ where $M$ is the metric fan space.
\end{thm}

@@

\begin{defn}
A space $X$ is \textbf{hemicompact} if there exists a chain of increasing compact sets $K_0\subseteq K_1 \subseteq \dots$ such that every compact set in $X$ is a subset of some $K_n$.
\end{defn}

\begin{lem}
If $K\prewin G_{K,P}(X)$, then $X$ is hemicompact. Furthermore, any predetermined winning strategy for $K$ witnesses hemicompactness.
\end{lem}

@@

\begin{thm}
The following are equivalent for any locally compact space $X$:
  \begin{itemize}
  \item $X$ is hemicompact.
  \item $K \prewin G_{K,L}(X)$.
  \item $K \prewin G_{K,P}(X)$.
  \end{itemize}
\end{thm}

@@

\begin{cor}
The following are equivalent for any locally compact space $X$:
  \begin{itemize}
  \item $X$ is Lindel\"of.
  \item $X$ is $\sigma$-compact.
  \item $X$ is hemicompact.
  \item $K \prewin G_{K,L}(X)$.
  \item $K \prewin G_{K,P}(X)$.
  \end{itemize}
\end{cor}

@@

\begin{defn}
A topological space is called a \textbf{$k$-space} if the following condition is satisfied: \[C \subseteq X \text{ is closed in } X\, \Leftrightarrow \, C\cap K \text{ is closed in } K \text{ for all compact sets } K\in K[X]\]
\end{defn}

\begin{defn}
A topological space is called a \textbf{$k_\omega$-space} if there exist $K_0,K_1,\dots \in K[X]$ that satisfy the following condition: \[C \subseteq X \text{ is closed in } X\, \Leftrightarrow \, C \cap K_n \text{ is closed in } K_n \text{ for all } n\]
\end{defn}

\begin{thm}
The following are equivalent for any Hausdorff $k$-space $X$:
  \begin{itemize}
  \item $X$ is hemicompact.
  \item $X$ is $k_{\omega}$.
  \item $K \prewin G_{K,P}(X)$.
  \end{itemize}
Furthermore, all predetermined strategies for $K$ witness hemicompact and $k_\omega$, and any witness to hemicompact/$k_\omega$ witnesses the other and serves as a predetermined strategy for $K$.
\end{thm}

@@

\begin{thm}
For any hemicompact Hausdorff $k$-space $X$, $K \prewin G_{K,L}(X)$.
\end{thm}

@@

\begin{cor}
The following are equivalent for any Hausdorff $k$-space $X$:
  \begin{itemize}
  \item $X$ is hemicompact.
  \item $X$ is $k_{\omega}$.
  \item $K$ has a winning predetermined strategy in $G_{K,L}(X)$.
  \item $K$ has a winning predetermined strategy in $G_{K,P}(X)$.
  \end{itemize}
\end{cor}

@@

\begin{defn}
Given a set $X$, an ultrafilter on $X$ is a collection $\mathcal{F}\subseteq\mathcal{P}(X)$ such that
    \begin{enumerate}
    \item $\emptyset\not\in \mathcal{F}$
    \item $A,B\in\mathcal{F} \Rightarrow A\cap B \in \mathcal{F}$
    \item $A\in\mathcal{F}$ and $A \subseteq B$ $\Rightarrow$ $B\in\mathcal{F}$
    \item $\forall A \subseteq X(A\in\mathcal{F}$ or $X\setminus A \in \mathcal{F})$
    \end{enumerate}
As a result, ultrafilters which contain a finite set contain only one singleton (and are called \textbf{principal}). Otherwise, ultrafilters which contain no finite sets are called \textbf{free}.
\end{defn}

\begin{defn}
The \textbf{Stone-Cech compactification} $\beta\omega$ of $\omega$ is the collection of ultrafilters on $\omega$. The principal ultrafilters containing a singleton $\{n\}$ are each identified with $n$ itself and are isolated. Free ultrafilters $\mathcal{F}$ are given neighborhoods of the form \[\{\mathcal{G} : \mathcal{G} \text{ is an ultrafilter on } \omega \text{ and } A \in \mathcal{G}\} = A \cup \{\mathcal{G}: \mathcal{G} \text{ is a free ultrafilter on } \omega \text{ and } A \in \mathcal{G}\}\] for each $A\in\mathcal{F}$.

Alternately $\beta\omega=\omega\cup\{\mathcal{F} : \mathcal{F}$ is a free ultrafilter on $\omega\}$ where $\omega$ is discrete and the free ultrafilters have the local base described above.
\end{defn}

\begin{defn}
A \textbf{single-ultrafilter space} is a subset of $\beta\omega$ containing all elements of $\omega$ and a single ultrafilter $\mathcal{F}$.
\end{defn}

\begin{prop}
The compact sets of a single-ultrafilter space are exactly the finite subsets of the space. Thus a single-ultrafilter space is neither locally compact nor $k$.
\end{prop}

@@

\begin{prop}
If $X$ is any single-ultrafilter space with the ultrafilter $\mathcal{F}$, then $K\not\prewin G_{K,L}(X)$.
\end{prop}

@@

\begin{prop} 
If a selective ultrafilter $\mathcal{F}$ exists (this is independent of ZFC), then $K$ has no winning predetermined strategy in the compact-point game $G_{K,P}(Y)$ for the single selective ultrafilter space $Y=\omega \cup \{\mathcal{F}\}$.
\end{prop}

@@

\begin{thm}
Let $a_n$ be a sequence such that the sequence $\frac{a_n}{n}$ is unbounded above. Then there is an ultrafilter $\mathcal{F}$ such that $\sigma(n)=(\sum_{m\leq n} a_m )\cup \{\mathcal{F}\}$ is a winning predetermined strategy for $K$ in $G_{K,P}(\omega\cup\{\mathcal{F}\})$.
\end{thm}

@@

\begin{ques}
$K \prewin G_{K,L}(X) \Rightarrow X$ is a $k$-space?
\end{ques}

\section{Cantor space example}

\begin{ex}
Let $X$ be a zero-dimensional, compact L-space (hereditarally Lindeloff and non-separable). It is a fact that there exists a point-countable collection $\mathcal{U}=\{U_\alpha : \alpha<\omega_1\}$ of clopen sets in $X$, and it is also true that any point-finite subcollection of $\mathcal{U}$ is countable. %That is, if we let $A_x = \{\alpha : x \in U_\alpha\}$, then $|A_x|\leq\omega$ for all $x\in X$.

Let $C = \{c_\alpha : \alpha <\omega_1\}$ be any uncountable subset of the Cantor space $2^\omega$. Let $X_s = X \times \{s\}$ for each $s \in 2^{<\omega}$, and $U_{\alpha,s} = U_\alpha \times \{s\}$.

Finally, let \[\mathbb{X} = C \cup \bigcup_{s\in 2^{<\omega}} X_s\] be a tree of $2^{<\omega}$ copies of $X$, and where \[c_\alpha \cup \bigcup_{n < \omega} U_{\alpha, x_\alpha \restriction n}\] is an open set about each $c_\alpha$.
\end{ex}

\begin{defn}
Let $S\in[\omega_1]^{<\omega}$ and $m<\omega$. Define 
    \[K_S = \bigcup_{\alpha \in S} \left( c_\alpha \cup \left(\bigcup_{s < c_\alpha} U_{\alpha,s}\right)\right)\] 
    \[ A = \{z^\frown \<1\> : z \in 1^{<\omega}\}\] 
    \[ K^*_S = K_S \setminus \bigcup_{s \in A} X_s \] 
and 
    \[L_m = \bigcup_{s \in 2^{<m}} X_s\] 
and observe that every compact set is dominated by $K^*_S \cup L_m$ for some $S,m$. Intuitively, $K^*_S$ collects the branches of $U_\alpha$ converging up to $c_\alpha$ for each $\alpha \in S$ while avoiding copies $X_s$ of $X$ for each $s$ in an antichain $A$, and $L_m$ collects the copies $X_s$ of $X$ with $|s| < m$ at the base of the tree.
\end{defn}

\begin{prop}
Without loss of generality, $P$ always plays points in $\bigcup_{s \in 2^{<\omega}} X_s$.
\end{prop}

\begin{prop}
$K \win \lfkpgame{\mathbb{X}}$.
\end{prop}

\begin{proof}
In response to a point $\<x,s\>$, $K$ observes that there are only countably many $\alpha$ such that $U_\alpha \times \{s\}$ contains $\<x,s\>$ (by point-countability of $X$). Enumerate these as $\alpha_n$. $K$ makes a promise that during round $m$, $K$ will forbid some superset of $K_{\{\alpha_n : n\leq m\}}$. Finally, $K$ also always forbids a superset of $L_{|s|+1}$.

Suppose $P$'s moves clustered at some point. Since $K$ forbade $L_{|s|+1}$ during each round, that point must be $c_\alpha$ for some $\alpha$. $P$'s play then must have included a subsequence of points $\<x_0,s_0\>,\<x_1,s_1\>,\<x_2,s_2\>\dots$ such that $x_n \in U_\alpha$ and $s_n \leq s_{n+1} \leq c_\alpha$. However, in response to $\<x_0,s_0\>$, $K$ made a promise to eventually forbid a superset of $K_{\{\alpha\}}$, making every $\<x_n,t_n\>$ illegal after that round.
\end{proof}

\begin{thm}
$K\not\tactwin\lfkpgame{\mathbb{X}}$.
\end{thm}

\begin{proof}
This is actually a corollary of G's theorem in [?]. The following is a direct game-theoretic proof.

Suppose that $\sigma(\<x,s\>)$ was a winning strategy for $K$ and assume 
  \[
    \sigma(\<x,s\>) = \bigcup_{|t|\leq |s|} \sigma(\<x,t\>) = \sigma'(x,|s|)
  \]
Thus there exists some $f: \omega_1 \to \omega$ such that $\sigma'(x,f(\alpha))$ covers every neighborhood of $c_\alpha$ for all $x\in U_\alpha$. (If not, $P$ wins by taking the $\alpha$ for which $f$ is not defined, and may always play $\<x,s\>$ in a neighborhood of $c_\alpha$ for which $\sigma'(x,|s|)$ doesn't cover a neighborhood of $c_\alpha$.) Fix $n$ for which $f(\alpha)=n$ for $\alpha$ in an uncountable set $A$.

Since the collection $\{U_\alpha : \alpha \in A\}$ is uncountable, it is not point-finite. Fix $x$ so that $x$ belongs to $U_\alpha$ for all $\alpha$ in an infinite $B \subseteq A$. Finally, consider $\sigma'(x,n)$. For each $\alpha\in B$, $\sigma'(x,f(\alpha))=\sigma'(x,n)$ covers $c_\alpha$. Since $\{c_\alpha : \alpha \in B\}$ is a closed infinite discrete set, we have a contradiction to the compactness of $\sigma'(x,n)$.
\end{proof}

\begin{thm}
$K\not\ktactwin{2}\lfkpgame{\mathbb{X}}$.
\end{thm}

\begin{proof}
Suppose $\sigma(\<x,s\>,\<y,t\>)$ was a winning 2-tactical strategy. We may define $S(x,y,n)\in [\omega_1]^{<\omega}$ (increasing on $n$) and $n<m(x,y,n)<\omega$ such that for each $(x,y)$,
  \[
    \bigcup_{s,t \in 2^{\leq n}} \sigma(\<x,s\>,\<y,t\>) \subseteq 
    K^*_{S(x,y,n)} \cup L_{m(x,y,n)}
  \]
and so we assume
  \[
    \sigma(\<x,s\>,\<y,t\>) =
    K^*_{S(x,y,\max(|s|,|t|))} \cup L_{m(x,y,\max(|s|,|t|))}
  \]

Select an arbitrary point $x' \in X$. We define a tactical strategy 
  \[
  \tau(x,s) = 
  K^*_{S(x,x',m(x,x',|s|)+1)} \cup L_{m(x,x',m(x,x',|s|)+1)}
  \]
We complete the proof by showing $\tau$ is a winning tactical strategy (a contradiction).
